\documentclass{article}
\usepackage[utf8]{inputenc}

\author{Dave Rozen}
\title{Legend Lore}
\begin{document}


\begin{abstract}
Open ended Attribute Based Extensible Role Playing
\end{abstract}

\section{Introduction}

Introduction to open ended gaming requires group participation and creativity. The goal of this topic is to  channel forward creative impetus and design using team building and paraphernalia for a  role playing game.

Team Building and Paraphernalia are coaxial greases used to flow facilitate game play in the environment of imaginable play. Each adventure module and game implementation are up to the endeavoring cast of participants in the game.

\section{Legend Lore}

Legend Lore is an open ended extensible attribute based role playing tabletop adventure game. It is design for free form adventure role-playing also structured or customized games as well.

This Game is designed for the purpose of facilitating creative storytelling involving a series of player characters and a main or assistant game-moderator (as such). The goal of such adventuring is to find exploration, creativity, storytelling, excitement, and challenge.

Above all have fun using these rules to facilitate your storytelling adventure games.

\section{The Role Player's Guide to Open Ended Gaming}

Created By Dave Rozen

(c) 2006 Drozen Dezine All Rights Reserved

A Note from the Author:

This Work is a collective Guide to enhance the flow of adventure in a role playing game. The goal of this book is to enhance the reader's ability to portray the high level of adventure and excitement found in role playing games. Legend Lore is an Open Ended, Extensible, Attribute Based, Adventure Game. In order to improve your gaming experience it is advised herein to learn the guidelines established in the material.

There are a few premises to consider about making an exciting adventure game. First Ask, Is the game leader enthusiastic and proactive about being part of the constructiveness found of the adventure? Next are the pool of players cooperative and intrigued? Finally ask, are the rules to my game a guideline avoiding any hindrance to how a well established adventure game should be played?

It is my hope that this book will facilitate and expand upon your adventuring in the realm of creative fantasy imagination.

~Best Regards, Dave Rozen.

\section{Adventure Role Playing}

Creating Adventure requires a bit of genius, ingenuity, and taste to make your game function in the idea of adventure, use your inner guidance to participate in such play!

\section{The Attribute Framework}

A rule set of cooperative and effective guidelines are known herein as Game play Implementations. Making fun rules that propel exciting game play requires ingenuity and continuity. That is, the rules to the game must make sense and follow a fair and concise guideline. These guidelines must adhere to the ideal of enhancing the fun of the game. In essence, Legend Lore role playing suggest that teaching gaming group fabricate the own preferable game implementation of rules.

The players and the Group Leaders are not alone; this book will educate the player base on crucial factors in making your game open ended. When the game is open ended, then that means it includes rule factors that facilitate play and act as a purposeful guideline to the welfare of working game play.

Ideal rules do not hinder the fun of the game but instead corroborate with the players and group leader's interests; also  these rules are fair and logical. Making the rules on topic of facilitates requires some insight into what works for the interests of the gaming group. When making effective Rule-sets, consider the following trends is extensible gaming: Do the Game Tokens all adhere under the same Guidelines?

Do the Characters have effectiveness in measurable strengths and checkpoints to operate  in the game?

\section{Tokens}

Active play samples of game content break out into forms of outcome effectiveness meant to act as a reward for player achievement and use a fair way to advance the characters along.  A game's structure sets a series of play rules to actively adjudicate the game decisions. The greater the odds in favor of outcome effectiveness the more of a chance the player has in succeeding. This implies that more powerful attributes receive a higher Token Pool. Tokens are represented by variable attribute delineations.

Higher Token Pools mean more Tokens in usefulness in outcome of adventure synopsis, Weaker Token Pools reduce successful resultants on a chance attempt against a harder Challenge Rating, that is pool of opposite effectiveness counteracting a Token Pool Success Rate. A Token Pool can be a number of Dominoes, Dice, Cards, Scrabble Crosswords (TM), Etc.

\section{Implementations}

The Main feature of an open ended gaming scenario is the use of Game Implementations. As Such, A Game Implementation is when a rule framework for Legend Lore can be applied to Legend Lore from another feasable Game Rule System using features like Tokens in the rule-set.  To Consider the outcome for the variable choice made by player characters and story characters the use of Tokens adjudicate how the game will result. Game Tokens and Source Tokens may act  involved in the main theme of the game with the official rules and the lingering options used by another game scenario.

Token examples set game play tools into representation of chance for Token Pools and Implimentation. Remember: A Token takes many sides, a dice peice such as a a game Die, Cards, Such as Uno cards, a Domnio (as found in gaming tools) or Mudra.

\section{Adventure Rule System Guidelines}

Role Playing Games can be played in a variety of styles, and gaming possiblities are as endless as the cooprative pairing within the gaming system and rule sets that the gamer facilitates into organized play. The Group Leader acts as a a guide and judge determining the outcome of each game scenario. To factor each game round, the Group Leader evaluates the effectivness of the Token Pool of Game Tokens, a game token has a score that ranges from marginal failure based on a low resultant scoring or harrowing acheivment cited by a higher token resultant scoring.

Tokens can multiply occur in a large variety of methods, such as Dice, Dominoes, Cards, Collectable Card Games, and even Mudras. (Mudras are hand gestures...)

Some verified Open Ended Game Systems include the rules of other games to facilitate pay, you will learn ways to participate in gaming in an Open Ended Role Playing Game alongside other games such as Uno(tm), Rummy or Gin Rummy, Poker, Dungeons and Dragons(TM), OGL D20, White Wolf(tm), D6 and Magic the Gathering(TM). Sofware found on the computer can be sued to impliment with games like Trip Zee (C) (a free Yatzze (TM) Game) To play alongside with a Game Play Implimentation using The Attribute Framework a rule system used in this book is sugested to Facilitate Gaming.

\section{Attribute Definitions}
An Attribute acts like a Descriptor of features for a character portraied in the story of the game. Such attributes define the character role and abilities. The introduction of Legend Lore Attributes are tied to the context of the game as a guide to introduce you to the helpfulness found in Attribute Role Playing.

The Attributes in Legend Lore Play are called, Purnam, Atma, Self, Mana, and Natural.

The Attributes make the most utilization of Legend Lore Gaming

\section{Legend Lore Attribute Rule System}

\subsection{Purnam}

The first attribute is called Purnam. Purnam is an ancient word that means complete, as in the unifying feature of completeness. In the properties of the game world, Purnam modifies the attribute rule set by granting additional tokens alongside a challenge factor provided they use the attribute in game play usable context.

Purnam represents the highness of godhead and divinity God seen as a Person, is supreme in all qualities of piety, beauty, knowledge, fame, power, and opulence eternally. Dvininity is our personal power of religiosity.

According to the Purnam Attribute; its relation to the The Collectible Trading Card Game Magic the Gathering(tm), Purnam is like White Mana and is consider Transcendental Spirit and is the Keeper of the Feilds.

\subsection{Atma}

The next attribute is atma, This attribute represents Spirit or Soul.

As a soul it is the empower factor that orchestrates the center abilities of the Player or Story Character. Atma represents Absolute Reality and is considered Green Mana in the TCG Magic the Gathering(TM),  Atma is the Retainer of Lushes, (or Forrest).

Atma refers to the soul, the absolute being of us. It is spirit and connected to nature. It is the receptacle to achieve our higher being, through surrender to Supersoul. Atma is a spirtual marginal energy that is our real self. Atma is enveloping force that defines the outside world and our relationship to it.


\subsection{Self}

The Self Attribute represents the Duality of Material Nature, this attribute is the characters identity. The Self Attribute explains what the character's core curriculum of abilities are and how they influence the player's actions. Self represents Black Mana, in Magic the Gathering(TM) and is the Guardian of the Marshes.

The Self, represents absolute and relative reality as induction and . it is part of us in constant change, the will and was. It defines, empowers, yet limits us. The self attribute determines what we are, what we result from our desired outcomes in qualification and in otherwise form.

\subsection{Natural}

The Mana Attribute is the attribute of Supernaturalism. This criterion attribute explains the unique talents and abilities of the User Player Character. The Mana Attribute is used as Blue Mana in the TCG: Magic the Gathering(TM) and represents island Land as the Ethereal House of Aquatics.

The Natural Attribute is the foundational Attribute, this Attribute defines all the features the character possesses within their mortal frame, and this is the Attribute of Material Nature.

This generalized attribute represents Red Mana or Volcano Land in the TCG: Magic the Gathering(tm) and is the master of the Earthen.

Our Corporeal Being of Energies and Mass. Naturalism is the embodiment of form in one kind or another. It is a connected unit in oneness of it all. Mortal, all beings in this way are mortal in tentativeness and susceptibility.

\subsection*{Natural Attribute Ability Scores}

Power
\begin{itemize}
\item Muscle, the enforcement of raw physical power
\item Endurance, the continuity of applied force.
\end{itemize}

Range
\begin{itemize}
\item Coordination, the manual abilities and aim of intracity
\item Flexibility, range of motion and control
\end{itemize}

Durability
\begin{itemize}
\item Vitality, the reverberation of dealing with extreme stressors
\item Health, the physical wellbeing of oneself.
\end{itemize}

Sociality
\begin{itemize}
\item Appearance, The visual attractiveness of oneself.
\item Charm, the ability to manipulate others socially.
\end{itemize}

Stature
\begin{itemize}
\item Build, the height and weight of the character.
\item Size, the status elements involving body range
\end{itemize}

Movement
\begin{itemize}
\item Speed, distance to be covered in action round.
\item Decisivenesses, foresight of reaction to encounters.
\end{itemize}

\subsection{Mana}

The Mana Attribute is the attribute of supernaturalism. This attribute explains the unique talents and abilities of the player characters. The mana attribute is used as blue mana in the TCG: Magic the Gathering(tm) and is the represents island land as Ethereal House of Aquatics.

Mana involves the mind, psychic regions, and relation to the unified field of all possibilities. The expectational aspect of influence on the outside world, the force will gather and reflect respectively.

Mana is the part of us that accepts and reject. Mana is the interpretation of the outside world.

\section{Progress Points}

A progress point is a reward given as a superlative achievement for a significant success utilizing a specific attribute. Such reweds can be spent towards earning an Attribute Token, or can be used in one time bonus rounds towards the token pool, limit 1 per check.

25 Progress Points earned towards Purnam upgrade an equivalent to 1 Purnam Token

20 Progress Points earned towards Atma upgrade equivalently to 1 Atma Token

15 Progress Points earned towards Self upgrade into an equivalent 1 Self Token

10 Progress Points earned towards Mana, upgrade an equivalent to 1 Mana Token

5 Progress Points earned towards Natural upgrade an equivalent to 1 Natural Token

It is congenial to award a player character Progress in their Attribute Prerogative Achievements.

\section{Legend Lore with UNO(TM)}

When a card is played, the numerical factors on the card determine how elaborately the card's specific color (or Attribute) influences play. The player drops the card down on the stack and records the attribute score

The Attribute Score is a collection of points gathered from play on the stack of cards, as the points are accumulated, a token can be played.

Each card color represents an attribute .

Yellow cards are Purnam, Green Cards are Atma, Wild Cards are 5 points in Self for basic and 10 Self for Wild Draw 4, Blue Cards are Mana Red Cards are Natural

Collect cards that are three of a kind to score an action 3 of a color or same number

3 of a kind can also be a flush of the same color

Follow suit in the pile and calculate the points on the cards to determine effectiveness.

To use Uno(TM) with Legend Lore remember the rules of the game play are already a lot like Uno(TM) but also you are to role play and are keeping score of the cards action value (to determine the effectiveness of a character's actions) and experience points (for character progression).

First the Group Leader deals the cards out to the Players. Then the Group Leader places an Uno(tm) card face up as the starting card. Then each player takes turns placing Uno cards on the stack. If a Player has a matching card they can place it down  on the stack, if the card can follow suit then the player can place additional cards.

If only one card is place then the score on the card determine action effectiveness. Higher scores are produced by placing additional cards during your turn, but only as many as one suit (Three Cards). Players have an option of using the attribute of the Color of the Last Card on the stack but only when they choose to use this feature.

The number on the card determines how effective the player choices are, the higher the number the more effective their action is. To reward experience against a challenge in th game, issued by the Group  Leader or as a Player contending, determine how much higher the contention is verses the challenge cards.

The number of challenge verses the number of the contention is evaluated only as how much higher the score is against the card ranks.

Example: A red card with a nine as its number is only 3 points higher then a card with a 6. Thus the player earns 3 experience points.


\section{Legend Lore with Poker}

Legend Lore with Poker plays a lot like regular Poker, however there are a few differences that are used for cooperation with both table callings to the rule set. Instead of using gambling tokens the game allows us to bid from our experience or action pool. Each round a player receives 10 Experience points. After the bids are made the winner of the pot receives the points and uses them to spend on actions in the adventure.

\begin{itemize}
\item  Select a hand and bid points from the experience pool.
\item Highest hand collects the pot and the round action in Rank
\item At the end of the bid cycle, contend your hand as in poker
\end{itemize}

        > A Flush (three or more of a suit)
        > A Hand (two or more of the same number)
        
\begin{itemize}
\item  Position rank with experience points
\end{itemize}

	To play Legend Lore alongside Poker the player receives an experience pool of 1 decision point or 1 common token to contend with during each round of play. The player's must match the stake to contend in each round.  A player who has the highest hand gets the pot and is the first to react to the adventure choices. Each Player after that rank each decide in action . The greater the expenditure of experience the higher the action achieved in the game.
    
 \section{Legend Lore in Dungeons and Dragons or D20 OGL}

Legend Lore in Dungeons and Dragons or D20 OGL asks us to fabricate adventures similar to those found in a typical game however one may accommodate the rule set to include. 

Legend Lore game play functions in essence the Attributes of a Legend Lore character influences the game rules as a super set of rules that contribute to adventure gaming.



\section{LEGEND LORE IN DUNGEONS AND DRAGONS™ OR D20™ OGL}

	Legend Lore in Dungeons and Dragons ™ or D20™ OGL asks us to fabricate adventures similar
to those found in a typical game however one may accommodate the rule set to include. Legend
Lore game play functions. In essence the Attributes of a Legend Lore character influences the
game rules as a super set of rules that contribute to adventure gaming.

	Use the following guidelines to participate a LLRPG with Dungeons and Dragons™ OGL
D20™

Exchange attributes for ability scores.

Substitute the character’s Mana score and replace the ranking as the Intelligence Score.

Substitute the character’s Atma score and replace the ranking as the Wisdom Score.

Allow The Nature Attribute to reflect Dungeons and Dragons Ability Scores.

Roll dice like in Dungeons and Dragons™

Resultants follow the rules found in Legend Lore Gaming

\section{LEGEND LORE WITH D6™}

For every attribute point roll a d6 for resultant  Optionally 6s to explode into another die
roll.

Use the attribute system to determine the outcome.

\section{LEGEND LORE WITH MAGIC: THE GATHERING}

LLRPG with Magic: The Gathering™ uses rules from the cards to cooperate with the adventure
guidelines along a Legend Lore Role Playing Game. 

Each card has a power score in the top left hand corner.

For every Mana color point: o Add one attribute point.

For every Colorless point o Add one action point.

• Each player has two hands o A draw hand o A magic hand

• The Draw Hand is used in making game actions

• The Magic Hand is for utilizing magic effects in the game. For every Atma point allow
one card for the magic hand.

\section{LEGEND LORE WITH RUMMY}

• Dealer drafts 7 or 9 cards to each player

• 3 of a kind in a suit or a flush score points

• Numbered Cards are worth 5, Face Cards are worth 10, Aces 15.

• The Higher the token score the more effective the action.

\section{LEGEND LORE WITH DOMINOES™}

LLRPG Dominoes™

• Use a Domino as an Action Token. o The number of points on the Domino shows
effectiveness. o 1-12 dots on a domino rules the action effectiveness

• Match usable dominoes on the pile for each turn.

\section{Character Creation}

• (Self) Starting with self, describe your character in one word.
• (Atma) Explain with one word where self-derives it power.
• (Purnam) Determine how Atma gets its power and original.
• (Mana) Give yourself an ability stem to branch from.
• (Natural) Determine forces for the body.

\section{Open Ended Guidelines}

• Freeform play:
Allow every player to contribute environment based on the score of points that player can
produce.

• GM play:
Allow a Lore Master to contribute environment based on the points he or she can produce and in
addition to a draw able cardstock pool.

LEGEND LORE PLAY

Allow a Lore Leader to influence environments and use generators and pre made materials to
contribute to the Environment Plot Development.

\section{GAME PLAY PROPS}

Seek relevant actions that are pertinent to the nature of the players. Find environmental features
that match the play style of the players. Use materials found in popular media to influence plot
and environment to create unique stories and environments. Use Miniatures, Art, and Diorama to
create visual representations.

\section{ADVANCING PLAYERS}

• Reward experience out for the scores in the game.
• For every 100 points gain one action/self-point.
• For every 10 self-points allow tree branch development

DIVINIOS OR MATOS

Divinios Points to 10 self 1 Atma 10 Atma 1 Purnam.

Matos Points to 10 selF 1 Mana 10 Mana 1 Nature.

\section{SKILLS AND FEATS}

• Name a skill and its features at the cost of 100 experience points.

• Choose a relative and sensible attribute to relate the skill to (usually found in body).

• Name a Feat and its features at the cost of 500 experience points.

• Choose a relative and sensible attribute to relate the feat to (usually Atma or Mana).

\section{CAMPAIGN DESIGN}

• Record notes to influence later adventures

• Create plot hooks to perpetuate the story into new directions

• Use pre written materials and game generators to create stories.

• Think of ways to grab the player’s attention and further gaming.

• Tailor story development to involve the interests of the players.

	The goal of endeavoring to produce an enjoyable campaign world, consider the following topics:
Campaign design is not just world building. When a player creates a fantasy world the goal is not
just to include maps and population charts.

The goal is to create a place of wonder that intrigues the players into dreaming about such a
manifested place.

	Ideally this world will spark player interests. To achieve this feat think about the process of
fabricating imagination. Take the properties of imagination elements and fuse them together.
Large valuable Gems might be awe inspiring to the players but what if they grew from the trunks
of trees in a sacred forest protected by dragons?

	Try to understand this example as to configure your imagination for the fabrication of great
wonderment. The goal of creating a fantasy world is to inspire the wonder and awe of the
player’s imagination.

\section{GAME PLAY GUIDELINES}
	
    Creating effective game play during a Role Playing Session is an important feature to having fun
while role playing. Keep in mind that having a good time while playing is the most important
achievement of a role playing adventure. To make the game play enjoyable, consider the
following guidelines while playing your open ended game.

\section{CREATING DRAMATIC TENSION}

	If every achievement was easy to accomplish in the adventure there will be no challenge.
Challenge and Drama are important features to the story of an adventure game. One advantage
found in Legend Lore stile role playing is that one can easily decide the challenge factor for the
chosen character decisions.

\section{CREATING CHALLENGE FACTORS}

	A Challenge Factor includes the importance and difficulty of a desired resultant. For an easy
challenge consider using fewer tokens against the challengers’ to- ken score. For a fair challenge
consider creating an even number of tokens against the challenge. For a harder challenge utilize
more tokens for the challenge at a score of one or more tokens.

\section{TOKEN SCORE}

A Token Score is the number of usable counting devices used to relate the score of the game
resultant. Tokens can be dice, cards, or even dominoes or other game score finders.

\section{CREATING DRAMA}

	The Adventure Game requires the use of good storytelling that is inventive and pertinent to the
game. To Create Drama consider the features of a good story.

	Do the players have the capacity to effectively overcome the odds against them? Are the
characters heroic? Are their opponents worthy adversaries? Do the adversaries influence the
story in a way that makes the players want to get involved?

	Dramatic Tension Elements such as these and other focuses propel Drama and create the Game
Play that is sought after in an Adventure Game...

\section{CONSIDER STORYTELLING ELEMENTS}

	The Storytelling Elements of the Game make Adventuring fun. While telling an exiting story,
make sure the game makes the use of Dramatic Storytelling Elements found in the form of
Effective Narration. Heighten Tensions found in the scheme of the story. Utilize flavorful
descriptors of the details for the Story.

\section{ADVENTURE DEVELOPMENT}

• MODERATING

	To create a good adventure game there has to be dramatic tension, flavorful descriptors, and
opportunity for heroism. Players like to make their characters achieve dreams unfathomable
outside of imagination. The goal of every game is to ensure that the players have a good time
acting out their characters. If the players had fun that means the moderator did a good job;
additionally, also had fun.

	To tell an exciting story borrows from the themes of the classics and also from popular themes.
Ask yourself: What story elements will spark player interests, how will my characters create
distinction in the imagination of my players, why is the adventure going to exhibit dramatic
excitement, when should I unveil the details of my adventure, what are the details of the
scenery, what is the goal of each game session?

	Questions like these will make a good game moderator, make the adventure game fun for the
players, and will utilize the purpose of playing as adventure characters. If the Game
Moderator is involved in planning adventures, explaining rich details in scenery, and fairly
adjudicating the rules engine of the game you will have a good session.
Also a good Game Moderator can bring out the spirit of a well-played session. Piquing the
Players to role play their characters well, motivating the emotive responses of the story, and will
help guide the players into the understanding of how to play.

• INTRIGUING PLAYERS

	Grab the Players interest to adventure exceptional, evoking emotive interest to the story, and
guiding player into the mysteries of the adventure are all motives for the Game Moderator.
This strategy can involve the player base in better gaming and role play. Use story telling
elements that grab the players’ interest. Learn about the players and their characters and motivate
their involvement in the game by linking their interests to the enjoyment of the game.
Players want to be entertained, and their characters allow the player to act out fantasy storytelling
intrigue that allows them to step outside of their typical lifestyle.

	Use promotional story elements that make the most of the characters dynamic. Create a detail
rich, adventure laced, mystery that will motivate the players to stay involved in the story.

\section{WORLD BUILDING}

	Creating successful environments will make the most of your gaming experience.
Consider key elements to world building. Utilize factors such as terrain and how it influences
mood, theme, and game play. Create dramatic weather conditions to accommodate or hider the
players’ adventure difficulty. Making adventurous climate and scenery will improve dramatic
interest in the story.

	Asking yourself, the moderator, important questions on how you describe your imaginative
world will influence the excitement of the game. Detail features of beauty, awe, and macabre
outlook will reveal an ongoing tale that players will be gripped into participating in.
Sometimes the sheer inspiration of the scenery will motivate the player’s imagination. Think
about how a fantasy world can differ from our reality.

Example: Maybe a forest of crystal trees decorates a floating fortress. The key is to harness your
imagination and the opportunities for creative gaming will remain endless.

\section{FACTORS IN ROLE PLAYING}

	The mood of the characters, the influence of the story, the excitement of the action, and
the details of the sensory information will factor how exiting the game will be. Consider how to
create characteristics and realism for the Player Characters and Adventure Characters. Ask
yourself what unique features do the charater’s possess, how do their personalities influence and
contribute to the adventure, and how do these game inclusions perpetuate the story?

	Effective personalities in your character base will make the adventure more important to the
players. Think of ways to make the story characters important. Con- sider how the characters
participate in the game, do the characters hinder the player base? Are they allies? Do they
consider friendship important?
	
    Is there a neutral base to the characters’ action?

\section{ADVENTURE STORYTELLING}

	The Plot of an adventure will strongly influence how fun the game will be to the players. Stories
that are intriguing to the players will produce exceptional gaming experiences, not to mention
such games will be meaningful and evocative to the player’s sense of fun. To make the plot
pertinent to your session consider effective elements to storytelling.

	I have good news and bad news for you, the bad news is you can never master the elements to a
well-established adventure story. The good news is you can always improve, in the famous
words of great writers, a work of written prose is never finished it is merely abandoned.

	Preparation before an adventure will contribute into how well established your game session will
be. Reading and Writing preparations for the adventure will allow the group to have a wellplayed
session

	While this book does not have any plan to fully address all the elements to good storytelling we
will consider some of the important details to adventuring.

\section{CHARACTERS AND PLOT}

	Well-crafted character developments produce effective storytelling queues. Con- sider the quirks
the payers introduce to the game during the duration of an adventure game. Most heroic
characters have a taste for adventure; give the players leads that will prove them forward into the
adventure.

	Creating elements of danger, tension, mystery, and plot to grab the players and guide their
imagination into higher dynamics of adventure. Villainy, Thugs, and Malcontents challenge the
players in their goal of achieving feats of heroism. To defeat such icons in your story, the players
must press their characters into dramatic conquest to overcome such obstacles

\section{EFFECTIVE STORYTELLING ELEMENTS}

	Any good story has three different elements to the story, the prologue, the cli- max, and the
epilogue. During the prologue players volunteer their adventuring spirit into the satisfaction of
their characters’ motivations. The climax speaks of the highlight of dramatic tension: the final
battle between the heroes and the villains. During the epilogue Players are driven to factor the
outcome of the adventure, settling old disputes, and bringing peace back to the land they embark
in.

	Remember this aspect of gaming is never mastered, it is only perfected. Attributes vary as widely
as ones’ imagination can muster, remember some attributes do not make sense to belong to the
attribute stem. As mentioned in character creation pg. 10, one starts to flesh out their character
with the Core Attribute.

	The following information on attributes starts with a list of Core Attributes and considerable
attribute branches.

\section{ATTRIBUTE GUIDELINES}

	Along with the creation of Attribute definitions the characters’ descriptor and range of action is
described herein the attribute system. The first key to the formation of an Adventure Character is
allocating the Self Attribute definition along with branchlike Atma Attribute hierarchy and Mana

\section{Attribute polymorphism.}

	The difference between hierarchy and polymorphism are as follows: Hierarchy refers to the
superset of the characters’ self-attribute or in other words a higher power, while polymorphic
delineation is a subset of the self-attribute.

	The descriptors below are simple sample attribute definitions. Additionally, descriptors will be
used to explain their detail.

\section{SAMPLE ATTRIBUTE DEFINITIONS}

PUGILIST

	A Pugilist is a martial arts expert, the Pugilist studies and exercises feats of living might. To the
Pugilist one may fight with the strength of their limbs in furious might and speed. The Pugilist
can perform special studies of might unknown to most Heroes.

	The Pugilistic Hierarchy Attribute: Artistry is the descriptor that explains the citation of the
Pugilist’ Power. Artistry refers to the intrinsic wonder that is the Martial Art Form.
When one is a Master of Artistry said Hero is capable of amazing feats of greatness. To enhance
A Pugilist Hero the option of Discipline defines how the Pugilist must live as a Hero of
Composure.

	Discipline allows the Pugilist Hero to achieve feats of great Restraint and Self Control. The
Pugilist Hero is a master of Deftness the intrinsic nature recommended for a Pugilist. Deftness
describes the Hero as an exemplar of Martial Utility. As the Pugilist Hero is Deft so is his might
in combat and agility.

NAVIGATOR

	A Navigator is an expert in discovery and travel. Said Navigators often utilize the benefits of
Vehicles, such as Piloting an Aircraft, or Driving a Motorcycle. Navigators derive their talents
from Exploration. This attribute defines the Navigator as a Hero of wonder and exploit. The
Navigator seeks to uncover hidden mystery, rare treasure, and has a sense of adventure.
Navigators often develop specializations in Gymnastics to aid the Navigator in the travel of
ancient tombs and hideaways. Gymnastics allows the Navigator to scale difficult terrain.
The key factor of the Navigator is Wonder, The natural curiosity of the Navigator’s Wonder
Purnam causes the Navigator to seek exploratory adventure. The Cause of Wonder in a
Navigators life compels them to traverse the globe seeking objects of miraculous awe. The
Navigator is piqued by a natural curiosity, exploring rare understandings, learning, seeking the
next clue always perpetuates the gratitude of the Navigator, this attribute allows the Navigator to
seek and find.

MASTER
	A Master is an Expert in Weaponry. Blades, Clubs, and Piercing instruments fancy the Master as
ruler of combat. Masters are controlled by the whim of Technique. Masters capitalize on
Technique and its range of exponential heroism in weapon combat.

	Improvising harnesses a Master in combat. This intrinsic power allows the Master to turn just
about any object found in their surroundings into a deadly tool. Focus delineates the true nature
of a Master; this power allows the Master Hero to achieve feats of unparalleled achievement. The
Master utilizes Adaption in the purpose of their inner spiritual potency;
	
    Adaption rules the factors of the Master in their ability to achieve supernatural capacity.

MARKSMAN

	A Marksman is the master of the missile weapons. Such Marksman can precisely aim the use of
a bow or firearm. The Precision descriptor fleshes out the details of the great prowess of the
Marksman in their heroic accuracy. Responsiveness details how Precision and Marksmanship
reflects their control over manual intricacies, such as agility.

	Aim is the key factor in the way of a Marksman. Aim explains how the Marks- man can
overcome distance with the accuracy of a machine. Projection explains the Marksman’s capacity
to propel objects with such capacity.

CASTER’

	Caster’ possesses power over supernatural phenomenon. Caster’ use the power of Mental
Incantation to manipulate the power of spiritual phenomenon. Magic is the source of power for
Arcana.

	Said powers allow the Caster to overcome nature. Most Casters are Substantiators. Substantiation
allows an Casters to whim matter into the folds of space and time. Divination is a frequent
feature of the Casters allows such magicians to commune with spiritual nature. Demureism is the
eccentric electiveness that is the Casters; this attribute describes the Casters’ ability of amazing
will.

PRIEST

Priests are people of spiritual power. They commune with the inclusion of the absolute.
Priests are governed and empowered by Piety the force of faith and virtue. Prayer imbibes the
Priest with the capacity to overcome the obstacles of the mundane. Priests pay homage to the
supreme personality of godhead, Sri Krishna Bhagavan. Bhagavan is the descriptor of great
personality. In order to master the power of Spiritual Commutation, Priests practice Renunciation
that is the connection of spirit to the supreme whole Shri Krishna, Bhagavan.

RONIN

	Ronin are masters of secrets and intrigue, such personalities are commonly filching, sneaking,
and performing low profile acts. Ronins derive much power from Stealth.
Stealth, he attribute of the undetected. Stealth allows the Ronin to hide, back-stab, disappear, and
break perception, camouflage, shadow, and mystery.

	Ronins are masters of the Sleight Hand. Detection is rare in the sight of a Ronin sneaking. The
Sleight Attribute allows Ronins to operate undercover never yielding to the sight of public eye.
Although Ronins achieve feats frowned upon in the outside world Ronins are Heroes of Honor.
This achievement Honor is the prime respect to said Heroes. Ronins will not break their code in
the fear that they will stumble back to humble beginnings. While at the same time Ronins are
attributed to Cloak, the underground undercover force of counterculture. Ronins are unknown to
most and belong to secret organization and codes.

SAGE

	Sages are masters of understanding and occult. A Sage keeps great secrets and uncovers the
hideaways of the unknown. Sages are founded on the Attribute of Knowledge the feature of
understanding. Sages specialize in Lore that is to master the arts and sciences of ancient crafts.
Sages offer respect to Bhraman that is the unified field of all possibilities. Sages are peppered by
the relation and practices of Aesthetics. They take great delight in austerity and penance,
additionally the act of devotion.

MYSTICS

	Mystics imbibe the mastery of perfection through the act of devotion to Supersoul. Spirit is the
prime factor in the way of the Mystics. Mystics use the way of spirit to achieve great acts of
wonderment. The specialization of said powers is funneled into
Auspiciousness that is the relation of great achievement citied by God; Shri Krishna He Who is
Key as the Prime Factor of Existential Desire.

	Krishna, the all attractive one, is the fulfiller of desire. The relation of Krishna to the Mystic is
the favored desire of a Mystic Hero. Mystics revel in servitude to the Supreme Bhagavan, Shri
Krishna and offer him Devotion that is servitude granted out of love and surrender.

\section{LEGEND LORE}

HOMEBREW POWER RULES

BOOK II

Shorthand Notation for Role Playing Games. The key to Shorthand Notation Success is to
Collect Effectively, a bank on Tokens and Points.
Example: 12 points in Dominoes to the right creatively allows Points and Tokens are the tools to
withdraw such derivatives.

THREE FACTORS PRODUCE OUTCOME EFFECTIVENESS:

REWARDS, TOKENS: POINTS: ATTRIBUTE BONUSES FOR HARROWING
ACHIEVEMENTS

COUNTERS, STAND IN ATTRIBUTE POINTS USED TO ENHANCE
CHALLENGE FACTORS

CHALLENGE, TOKEN POOL VS. TOKEN POOL = SUCCESS / FAIL TESTS

These factors determine produce to range, score possibility to contentedness, forthcoming to
detriment. These congruities will allow progress via game narrative. The higher the score the
greater the derived forthcoming in gameplay. Failure also delineates weaker choices.
5TH EDITION DUNGEONS AND DRAGONS CO-OP

Strength Dexterity and Constitution all relate to Self - > 1 dDice, 2, dDice, *dDice

Intelligence Wisdom and Charisma relate to Atma, Purnam, and Mana 1*, 2*, and 3*
*represents score progress self-ranks progressively on attributes

\section{MAGIC THE GATHERING ™ CO-OP}

	When a card is activated with a Play Action, The Attributes determine the Score.
I.e 2 Mountains is equal to a play of Two Hearts, or Vitality Points in Play
Another Example is: One Plain is a call upon the score of your Supra as a single token bonus.
Be Flexible and Use the Rules that Favor you and above all Home-brew your Imagination.

\section{TOKENS}

Tokens provide a route of challenges, Having bonus tokens in or against your favor.
The scores have a slant but If you are equal scored than the player receives a bonus victory of 0.5

% bonus to win.

Tokens can be Dice Rolls: d20, d10, d6, d4 etc.

Tokens can Be Cards: King 15, Queen 12, Jack 11, Ten 10

Tokens can be Collectible Trade Card Games, Mountain x 2 Colorless: 3 = 7 pts.

Tokens can be Game Icons: Dominoes

\section{SPENDING EXPERIENCE POINTS}

	Experience comes from successes from Token Score Attributes Victories.
You gain experience points and can spend 0.5% cost vs. Your Experience points to spend a
Action Token Bonus.
TOKEN BONUS.
+1 bonus token 150% cost, Exp = Attribute
+3 bonus token 225% cost, Exp = Attribute
+5 bonus token 350% cost, Exp = Attribute
+9 bonus token 500% cost, Exp = Attribute

Each bonus is a one use, one trigger, on deduction and expires at the end of the game round.
EARNING EXPERIENCE

Earning Experience requires The Element of Risk, The Taking of Challenge, and The Dangers
found from Sticking your Neck Out.

Usually experience points are awarded 1 – 10 exp at a time.

The more achievements the more points earned real-time.

\section{LEGEND LORE, EARLY ADOPTIVE RULES}

This is a simple role playing game that entails role playing and chances resolved by dice. Aces
are high.

Take a sheet of paper and roll 6 dice. Score as follows lowest roll must score at Spade Bin (or
Supra) it is suggested that middle score appear at the Self stat chart.

\section{CARDS ARE FOR CHALLENGES.}

Rummy scores experience. Dice are for simple challenges.
1 mulligan for stats or card.

The card house is determined in order as such:
Spade Club Diamond Heart with the Self and its Merits as the Legend. Spade and Club
encompass Nature (Yang) while Diamond and Heart touches upon Nurture (Yin).
Spade represents Supra the highest of the high. It can be called upon for assistance at the
discretion of the Lore Leader. Supra grants lessor powers to Atma the powers that be within the
Legend.

The Club represents Atma. The Atma is the supernatural aspect of the Legend. Atma has power
and drawback depending on the choices agreed upon during the creation of the Legend.
Self is between the metaphysical spirit and humanity. Self is the center of the Legend.
Diamond faces mind. influences field, trigger and and dreams. Triggers determine the influence
of the mind. Fields are influences by that what is made so by the mind. Dreams are goals that can
be set in motion.

HEART MAKES UP THE BODY

Strength vrs Muscle
Vitality vrs Fortitude
Dexterity vrs Agileness

Scorecard Bonus: Volcano is Body, Island is Mind, Marsh is Self, Forest is Atma and Flatlands
is Supra.

For magic users who want to add to the game.

\section{GAMEPLAY IMPLEMENTATIONS}

	Legend Lore can be played in a variety of styles and the possibilities are as endless as you can
create feasible systems to implement.

	Some verified game systems include UNO™, Gin Rummi, Poker, Dungeons and Dragons™,
OGL D20, White Wolf™ D6, and Magic the Gathering™.

	Software found on the computer can be used to implement LLRPG games like tripZee (a free
Yahtzee game).

\section{CORE RULES OF LEGEND LORE}

	Attribute Definitions that define the role and abilities of a character.

The Supra, The Infinite and Keeper of the Fields.
The Atma, The Soul the Retainer of Lushes.
The Self, Identity guardian of the Marshes
The Mana, Ether house of the Tropics.
The Body, Matter master of The Earthen.

\section{CHARACTER DESCRIPTORS FOR ATTRIBUTE GAMING}

Supra, Represents the highness of godhead and divinity of a higher power seen as a person is
supreme in all qualities of piety, beauty, fame, power, and opulence eternally. Divinity is our
personal power of Religiosity

Atma, References the immortal soul, the absolute being of ourselves. It is spirit and connected
to nature. The receptacle to achieve our higher being, through surrender to super-soul.
Undependable energy that is our real self. The enveloping force that defines the outside world
and our relationship to it.

Self, Represents material nescience duality and the modes of material nature. The part of us in
constant change, the will and was. Defines, Empowers, yet Limits us. Determines what we are,
what results from our desired outcomes in qualification. Otherwise in form.

Mana, Involves the mind, psychic regions, and relation to the unified field of possibilities. The
extinguishable aspect of influence on the outside world this force will gather and report to
reflectively. The part of the us that accepts and rejects. Ability of the self to interpret the outside
world.

Body, Our Corporeal Being of energies and mass. Embodiment of form of one kind or
another. A connected unit in the oneness of it all. Mortal, all beings in this way are perdurable
because of tentativeness and susceptibility.

BODY SCORES

STRENGTH
Muscle, the enforcement of raw physical power
Endurance, the continuity of applied force

DEXTERITY
Coordination, the manual abilities and aim of intricacies
Flexibility, the range of motion and control.

CONSTITUTION
Vitality, the reverberation of dealing with extreme stresses.
Health, the physical well-being of oneself.

CHARISMA
Appearance, The visual attractiveness of oneself.
Charm, The ability to manipulate others socially.

STATURE
Build, The height and weight of the character.
Size, the status elements involving body range

MOVEMENT
Speed, The ability for distance to be covered.
Imitative, The foresight of reaction to encounters.

\section{CHARACTER CREATION}

Starting with Self, describe your character with one word.
Explain with one word ‘Self’ derives the power, of Atma.
Determine how Atma gains enabling power and origin, the Supra.
Designate your character with an ability descriptor for Skill Utilities and Feats. Mana scores as
such.

DETERMINE YIN AND YANG FORCES FOR BODY

+1 / +3 = Yang, Pandemonium Descriptors of Faith.
+3 / +1 = Yin, Pandora: Supernatural Power, Heroism.

SYMBOL CARD CONVERSIONS SCORE SHEET
 The Supra, The Infinite and Keeper of the Fields.
 The Atma, The Soul the Retainer of Lushes.
 The Self, Identity guardian of the Marshes
 The Mana, Ether house of the Tropics.
 The Body, Matter master of The Earthen.




\section{Open Ended Gaming}

Facility in organized play takes team building and inspiration for the participation of adventure sessions.

Open Ended Gaming requires one to utilize differing materials for facility in play of character and existence for the adventure scenario.

\subsection{Open Ended Extensible attribute based Role Play}

Use Freedom forming rules to compel your gaming environment further into game-play using paraphernalia   and team building gaming environments.

It is ideal to utilize participating adventure tools to organize the utilization of rules, citing for gaming, and adventure scenarios.

\section{Participation of Paraphernalia in Teaming}

Team Building works alongside the creation of usable content for Tokens and Gaming Paraphernalia.

Use Paraphernalia to make rule-sets and Tokens from adventure modules to allocate play.

\subsection{Utilizing Tokens as Paraphernalia}

The gaming materials used by adventure contents allows for the use of gaming props called tokens. Tokens are sums of items that produce outcomes that relay effectiveness of the activities for a chosen action in play. Like dominoes, cards, dice, optimization gaming tools. All can be used in outcome effectiveness in play.

\subsection{Teamwork in Orchestrating Ideas for Gaming}
Working together to partake in home-brew or affirmation ideas for the activities of an adventure game brings the gaming scenario into new horizons of facility in game play implementation. If you can bring it and it works it could be part your game and participant ideal.

\section{Detail for Imaginative Adventuring}
Utilizing imaginative congregational paraphernalia utilizes to goal to achieve goals for game production as a complementation to the adventure game Legend Lore.

\subsection{Maximizing Utility of Brainstormed Adventure Notes}
Gaming makes the most of imagination in a role play scenario. Utilizing rule-frame and participation of gaming setup allows open play and facilitates story and plot. 

\subsection*{Facilitating Gaming Interactive and Plot}
The story delimitations and plot participate in ongoing adventure symposium.
Participate in ongoing gaming

\subsection*{Creativity Synchrotron among Playgroup}
The play group consisting of player base, moderator, and modularize will participate the adventure creative synchrotron.
\end{document}documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
(Type your content here.)
\end{document}
